agdarsec -- Total Parser Combinators

### 2017-10-02 doc/paper/main.tex
[ doc ] start of refs

Last but not least, the \BOX{} type constructor takes a \AD{ℕ}-indexed
set and produces the one corresponding to the allowed recursive
calls in a function defined by course-of-values recursion: \BOX{}
\AB{A} \AB{n} associates to each \AB{m} strictly smaller than \AB{n}
a value of type \AB{A} \AB{m}.

@@

@@

%% Bibliography
%\bibliography{bibfile}

>>>>

Last but not least, the \BOX{} type constructor takes a \AD{ℕ}-indexed
set and produces the set of valid recursive calls for a function defined
by course-of-values recursion: \BOX{} \AB{A} \AB{n} associates to each
\AB{m} strictly smaller than \AB{n} a value of type \AB{A} \AB{m}.
This construct, analogous to the later modality showing up in Guarded
Type Theory~\cite{vezzosi2015guarded}, empowers the user to give precise
types in a total language to programs commonly written in partial ones
(see e.g. the definition of \textit{fix} below).

@@

\paragraph{Remark: Identifiers in Agda} In Agda, any space-free
string which is not a reserved keyword is a valid identifier. As
a consequence we can pick suggestive names such as \AB{m<n} for
a proof that $m < n$.

@@

%% Bibliography
\bibliography{main.bib}
